Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/theory_results.tex
widow line

{\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, except the approximation for $e^x$ is not needed.

>>>>

{\bf Proof Sketch of Lemma~\ref{lma:mult_lemma}} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma}, but without $e^x \approx 1+x$.
